---
title: "Project"
author: "Otunbade Jubril"
date: "4/16/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Continental Analysis of Youtube Videos

## North AMerica

### importing packages and datasets
```{r cars}
library(caret)
library(tidyverse)
library(comprehenr)
```

```{r}
US = read.csv('US-ok.csv')
CA = read.csv('CA-ok.csv')
MX = read.csv('US-ok.csv')
```

```{r}
NoA <- rbind(US,CA,MX)
glimpse(NoA)
```
The North American dataset contains a total of 122609 samples, 18 variabes of which 5 are integers while the rest are factor variables. 


### Descriptive Analysis
```{r}
summary(NoA)
```
In the integer variables, there exist large outliers i.e the values of the 3rd quartile and the maximum value are quiet far apart. This will cause a large skew in the mean of the integer variables.
The views variable as a minimum of 547 and a maximum of above 200M. The likes, dislikes and comment_count variables have maximum values in the millions and minimums of 0 which is possible when some of the videos are ratings_disabled, comments_disabled etc.
The most common categories is the Entertainment (33,339), Music (16,665) while the least categories are Movies, Nonprofit & Activism and Shows.

The description variable contains some missing values - 5968

To check for missing values in the data set

```{r}

```

### Feature Extraction
```{r}
NoA$trending_date = lapply(NoA$trending_date, function(w) paste(20, w, sep=''))
NoA$trending_date = lapply(NoA$trending_date, function(w) gsub("\\.", "/", w))
NoA$publish_time = as.POSIXlt(NoA$publish_time)

# Publish
P_years = substring(NoA$publish_time, 1, 4)
P_months = substring(NoA$publish_time, 6, 7)
P_days = substring(NoA$publish_time, 9, 10)

#Trending
T_years = substring(NoA$trending_date, 1, 4)
T_months = substring(NoA$trending_date, 9, 10)
T_days = substring(NoA$trending_date, 6, 7)

# Counts
NoT = to_vec(for(i in NoA$tags) nchar(split(i, '|')))
NoC = to_vec(for(i in NoA$title) nchar(gsub(' ', '', i)))
NoW = to_vec(for(i in NoA$title) nchar(split(i, ' ')))
Tags = to_vec(for(i in NoA$tags) split(i, '|'))
```

Some variables/column are of little important to the current exploratory Analysis. So they shall be dropped
```{r}
NoA <- NoA[, !(colnames(NoA) %in% c('thumbnail_link', 'category_id','video_id', 'description','assignable'))]
```
* Reasons:
 * Video_id : the values of this variable seems to be random characters of a string, it plays no important role
 * Category_id: The numerical values of this variable served as the key for merging the catergory variable. No longer needed
 * Thumbnail_link: this object datatype variable contains links to the thumbnail. Its of no use
 * Description : The variable gives the Description of the video or the channel and links. It contains all the missing values of the dataset
 * Assignables: The correlation of this variable to some of the more important variables gives a very low value


### Exploratory Analysis
```{r}
# Plot on category distribution
qplot(y = category, data = NoA, geom = 'bar')
# Plot on views distribution
qplot(views, data = NoA, bins = 100)
# Plot on likes distribution
qplot(likes, data = NoA, bins = 100)
# Plot on dislikes distribution
qplot(dislikes, data = NoA, bins = 100)
# Plot on comment_count distribution
qplot(comment_count, data = NoA, bins = 100)
# Plot on Number of Character distribution
qplot(NoC, data = NoA, bins = 210)
# Plot on Number of Words distribution
qplot(NoW, data = NoA, bins = 230)
# Plot on Number of Tags distribution
qplot(NoT, data = NoA, bins = 100)
```

```{r}
# Number of words vs views# Plot on category vs views based on ratings disabled or not
qplot(y = category, x = views, data = NoA, geom = 'auto', color = ratings_disabled)
# Plot on category vs views based on ratings disabled or not
qplot(likes, views, data = NoA, geom ='auto', color = video_error_or_removed)
qplot(comment_count, views, data = NoA, geom = c('smooth','auto'))
qplot(likes, views, data = NoA, geom ='auto', color = category)
qplot(comment_count, likes, data = NoA, geom =c('smooth','auto'))
qplot(comment_count, dislikes, data = NoA, geom =c('smooth','auto'))
```

```{r}
ggplot(NoA, aes(views,reorder(category,views))) + geom_col(position = 'dodge', fill = T_years)
```
From the above, the entertainment and the Howto & Style categories had more views (i.e. trended) in 2017 than in 2018. 
```{r}
# Trending months
qplot(T_months)
qplot(T_months, NoA$views)
qplot(T_months, NoA$likes)
qplot(T_months, NoA$comment_count)
qplot(T_months, NoC)
qplot(T_months, NoT)
qplot(T_months, NoW)

# Trending years
qplot(T_years)
qplot(T_years, NoA$views)
qplot(T_years, NoA$likes)
qplot(T_years, NoA$comment_count)
qplot(T_years, NoC)
qplot(T_years, NoT)
qplot(T_years, NoW)

# Trending days
qplot(T_days)
qplot(T_days, NoA$views)
qplot(T_days, NoA$likes)
qplot(T_days, NoA$comment_count)
qplot(T_days, NoC)
qplot(T_days, NoT)
qplot(T_days, NoW)
```

```{r}
# Publish days
qplot(P_days)
qplot(P_days, NoA$views)
qplot(P_days, NoA$likes)
qplot(P_days, NoA$comment_count)
qplot(P_days, NoC)
qplot(P_days, NoT)
qplot(P_days, NoW)

# Publish years
qplot(P_years)
qplot(P_years, NoA$views)
qplot(P_years, NoA$likes)
qplot(P_years, NoA$comment_count)
qplot(P_years, NoC)
qplot(P_years, NoT)
qplot(P_years, NoW)

# Publish months
qplot(P_months)
qplot(P_months, NoA$views)
qplot(P_months, NoA$likes)
qplot(P_months, NoA$comment_count)
qplot(P_months, NoC)
qplot(P_months, NoT)
qplot(P_months, NoW)
```

```{r}
# Number of Words
qplot(NoW, NoA$views)
# Number of characters vs views
qplot(NoC, NoA$views)
# Number of tags vs views
qplot(NoT, NoA$views)
```


```{r}
# Number of Tags vs number of words
qplot(NoW, NoT, data = NoA, geom = c('smooth','auto'))
```

```{r}
qplot(P_days,T_days)
qplot(P_months,T_months)
qplot(P_years,T_years)
```

## Europe
```{r}
FR = read.csv('FR-ok.csv')
DE = read.csv('DE-ok.csv')
GB = read.csv('GB-ok.csv')
RU = read.csv('RU-ok.csv')
```

```{r}
Europe <- rbind(FR,DE,GB,RU)
glimpse(Europe)
```
The European dataset contains a total of 159,003 samples, 20 variabes of which 5 are integers while the rest are factor variables


### Descriptive Analysis
```{r}
summary(Europe)
```
In the integer variables, there exist large outliers i.e the values of the 3rd quartile and the maximum value are quiet far apart

To check for missing values in the data set
```{r}
library(Amelia)
missmap(Europe, col=c("black", "grey"), legend=FALSE)
```

```{r}

```

### Feature Extraction
```{r}
Europe$trending_date = lapply(Europe$trending_date, function(w) paste(20, w, sep=''))
Europe$trending_date = lapply(Europe$trending_date, function(w) gsub("\\.", "/", w))
Europe$publish_time = as.POSIXlt(Europe$publish_time)

# Publish
P_years = substring(Europe$publish_time, 1, 4)
P_months = substring(Europe$publish_time, 6, 7)
P_days = substring(Europe$publish_time, 9, 10)

#Trending
T_years = substring(Europe$trending_date, 1, 4)
T_months = substring(Europe$trending_date, 9, 10)
T_days = substring(Europe$trending_date, 6, 7)

# Counts
NoT = to_vec(for(i in Europe$tags) nchar(split(i, '|')))
NoC = to_vec(for(i in Europe$title) nchar(gsub(' ', '', i)))
NoW = to_vec(for(i in Europe$title) nchar(split(i, ' ')))
```

Some variables/column are of little important to the current exploratory Analysis. So they shall be dropped
```{r}
Europe <- Europe[, !(colnames(Europe) %in% c('thumbnail_link', 'category_id','video_id', 'description','assignable'))]
```
* Reasons:
 * Video_id : the values of this variable seems to be random characters of a string, it plays no important role
 * Category_id: The numerical values of this variable served as the key for merging the catergory variable. No longer needed
 * Thumbnail_link: this object datatype variable contains links to the thumbnail. Its of no use
 * Description : The variable gives the Description of the video or the channel and links. It contains all the missing values of the dataset
 * Assignables: The correlation of this variable to some of the more important variables gives a very low value


### Exploratory Analysis

```{r}
# Plot on category distribution
qplot(y=category, data = Europe, geom = 'bar')
# Plot on views distribution
qplot(views, data = Europe, bins = 100)
# Plot on likes distribution
qplot(likes, data = Europe, bins = 100)
# Plot on dislikes distribution
qplot(dislikes, data = Europe, bins = 100)
# Plot on comment_count distribution
qplot(comment_count, data = Europe, bins = 100)
# Plot on Number of Character distribution
qplot(NoC, data = Europe, bins = 210)
# Plot on Number of Words distribution
qplot(NoW, data = Europe, bins = 230)
# Plot on Number of Tags distribution
qplot(NoT, data = Europe, bins = 100)
```

```{r}
# Number of words vs views# Plot on category vs views based on ratings disabled or not
qplot(y = category, x = views, data = Europe, geom = 'auto', color = ratings_disabled)
# Plot on category vs views based on ratings disabled or not
qplot(likes, views, data = Europe, geom ='auto', color = video_error_or_removed)
qplot(comment_count, views, data = Europe, geom = c('smooth','auto'))
qplot(likes, views, data = Europe, geom ='auto', color = category)
qplot(comment_count, likes, data = Europe, geom =c('smooth','auto'))
qplot(comment_count, dislikes, data = Europe, geom =c('smooth','auto'))
```

```{r}
qplot(y = category, data = Europe, geom  = 'bar', fill= substring(trending_date, 1, 4), position = "dodge")
```

```{r}
# Trending months
qplot(T_months)
qplot(T_months, Europe$views)
qplot(T_months, Europe$likes)
qplot(T_months, Europe$comment_count)
qplot(T_months, NoC)
qplot(T_months, NoT)
qplot(T_months, NoW)

# Trending years
qplot(T_years)
qplot(T_years, Europe$views)
qplot(T_years, Europe$likes)
qplot(T_years, Europe$comment_count)
qplot(T_years, NoC)
qplot(T_years, NoT)
qplot(T_years, NoW)

# Trending days
qplot(T_days)
qplot(T_days, Europe$views)
qplot(T_days, Europe$likes)
qplot(T_days, Europe$comment_count)
qplot(T_days, NoC)
qplot(T_days, NoT)
qplot(T_days, NoW)
```

```{r}
# Publish days
qplot(P_days)
qplot(P_days, Europe$views)
qplot(P_days, Europe$likes)
qplot(P_days, Europe$comment_count)
qplot(P_days, NoC)
qplot(P_days, NoT)
qplot(P_days, NoW)

# Publish years
qplot(P_years)
qplot(P_years, Europe$views)
qplot(P_years, Europe$likes)
qplot(P_years, Europe$comment_count)
qplot(P_years, NoC)
qplot(P_years, NoT)
qplot(P_years, NoW)

# Publish months
qplot(P_months)
qplot(P_months, Europe$views)
qplot(P_months, Europe$likes)
qplot(P_months, Europe$comment_count)
qplot(P_months, NoC)
qplot(P_months, NoT)
qplot(P_months, NoW)
```

```{r}
# Number of Words
qplot(NoW, Europe$views)
# Number of characters vs views
qplot(NoC, Europe$views)
# Number of tags vs views
qplot(NoT, Europe$views)
```


```{r}
# Number of Tags vs number of words
qplot(NoW, NoT, data = Europe, geom = c('smooth','auto'))
```

```{r}
qplot(P_days,T_days)
qplot(P_months,T_months)
qplot(P_years,T_years)
```


## Asia
### importing datasets
```{r}
KR = read.csv('KR-ok.csv')
JP = read.csv('JP-ok.csv')
IN = read.csv('IN-ok.csv')
```

```{r}
Asia <- rbind(KR, JP, IN)
glimpse(Asia)
```
The Asian dataset contains a total of 79,801 samples, 18 variabes of which 5 are integers while the rest are factor variables


### Descriptive Analysis
```{r}
summary(Asia)
```
In the integer variables, there exist large outliers i.e the values of the 3rd quartile and the maximum value are quiet far apart

To check for missing values in the data set
```{r}
library(Amelia)
missmap(Asia, col=c("black", "grey"), legend=FALSE)
```

```{r}

```

### Feature Extraction
```{r}
Asia$trending_date = lapply(Asia$trending_date, function(w) paste(20, w, sep=''))
Asia$trending_date = lapply(Asia$trending_date, function(w) gsub("\\.", "/", w))
Asia$publish_time = as.POSIXlt(Asia$publish_time)

# Publish
P_years = substring(Asia$publish_time, 1, 4)
P_months = substring(Asia$publish_time, 6, 7)
P_days = substring(Asia$publish_time, 9, 10)

#Trending
T_years = substring(Asia$trending_date, 1, 4)
T_months = substring(Asia$trending_date, 9, 10)
T_days = substring(Asia$trending_date, 6, 7)

# Counts
NoT = to_vec(for(i in Asia$tags) nchar(split(i, '|')))
NoC = to_vec(for(i in Asia$title) nchar(gsub(' ', '', i)))
NoW = to_vec(for(i in Asia$title) nchar(split(i, ' ')))
```

Some variables/column are of little important to the current exploratory Analysis. So they shall be dropped
```{r}
Asia <- Asia[, !(colnames(Asia) %in% c('thumbnail_link', 'category_id','video_id', 'description','assignable'))]
```
* Reasons:
 * Video_id : the values of this variable seems to be random characters of a string, it plays no important role
 * Category_id: The numerical values of this variable served as the key for merging the catergory variable. No longer needed
 * Thumbnail_link: this object datatype variable contains links to the thumbnail. Its of no use
 * Description : The variable gives the Description of the video or the channel and links. It contains all the missing values of the dataset
 * Assignables: The correlation of this variable to some of the more important variables gives a very low value


### Exploratory Analysis

```{r}
# Plot on category distribution
qplot(y=category, data = Asia, geom = 'bar')
# Plot on views distribution
qplot(views, data = Asia, bins = 100)
# Plot on likes distribution
qplot(likes, data = Asia, bins = 100)
# Plot on dislikes distribution
qplot(dislikes, data = Asia, bins = 100)
# Plot on comment_count distribution
qplot(comment_count, data = Asia, bins = 100)
# Plot on Number of Character distribution
qplot(NoC, data = Asia, bins = 210)
# Plot on Number of Words distribution
qplot(NoW, data = Asia, bins = 230)
# Plot on Number of Tags distribution
qplot(NoT, data = Asia, bins = 100)
```

```{r}
# Number of words vs views# Plot on category vs views based on ratings disabled or not
qplot(y = category, x = views, data = Asia, geom = 'auto', color = ratings_disabled)
# Plot on category vs views based on ratings disabled or not
qplot(likes, views, data = Asia, geom ='auto', color = video_error_or_removed)
qplot(comment_count, views, data = Europe, geom = c('smooth','auto'))
qplot(likes, views, data = Asia, geom ='auto', color = category)
qplot(comment_count, likes, data = Asia, geom =c('smooth','auto'))
qplot(comment_count, dislikes, data = Asia, geom =c('smooth','auto'))
```

```{r}
qplot(y = category, data = Asia, geom  = 'col', fill= T_years, position = "dodge")
```

```{r}
# Trending months
qplot(T_months)
qplot(T_months, Asia$views)
qplot(T_months, Asia$likes)
qplot(T_months, Asia$comment_count)
qplot(T_months, NoC)
qplot(T_months, NoT)
qplot(T_months, NoW)

# Trending years
qplot(T_years)
qplot(T_years, Asia$views)
qplot(T_years, Asia$likes)
qplot(T_years, Asia$comment_count)
qplot(T_years, NoC)
qplot(T_years, NoT)
qplot(T_years, NoW)

# Trending days
qplot(T_days)
qplot(T_days, Asia$views)
qplot(T_days, Asia$likes)
qplot(T_days, Asia$comment_count)
qplot(T_days, NoC)
qplot(T_days, NoT)
qplot(T_days, NoW)
```

```{r}
# Publish days
qplot(P_days)
qplot(P_days, Asia$views)
qplot(P_days, Asia$likes)
qplot(P_days, Asia$comment_count)
qplot(P_days, NoC)
qplot(P_days, NoT)
qplot(P_days, NoW)

# Publish years
qplot(P_years)
qplot(P_years, Asia$views)
qplot(P_years, Asia$likes)
qplot(P_years, Asia$comment_count)
qplot(P_years, NoC)
qplot(P_years, NoT)
qplot(P_years, NoW)

# Publish months
qplot(P_months)
qplot(P_months, Asia$views)
qplot(P_months, Asia$likes)
qplot(P_months, Asia$comment_count)
qplot(P_months, NoC)
qplot(P_months, NoT)
qplot(P_months, NoW)
```

```{r}
# Number of Words
qplot(NoW, Asia$views)
# Number of characters vs views
qplot(NoC, Asia$views)
# Number of tags vs views
qplot(NoT, Asia$views)
```


```{r}
# Number of Tags vs number of words
qplot(NoW, NoT, data = Asia, geom = c('smooth','auto'))
```

```{r}
qplot(P_days,T_days)
qplot(P_months,T_months)
qplot(P_years,T_years)
```